Analysis

### 2020-01-16 script/analysis.Rmd
interaccion año*gaper /  descriptivos stargazer
i

@@

>>>>

## 1999-2019 con interaccion. 
```{r}
load("input/data/processed/clw3.Rdata")
#sjPlot::view_df(clw3)

rta<-lm(lngap_perc ~ + as.factor(educ_rec) + as.factor(Quint) + as.factor(year), data=clw3)
rtb<-lm(lngap_just ~ + as.factor(educ_rec) + as.factor(Quint) + as.factor(year), data=clw3)
rtc<-lm(lngap_just ~ + as.factor(educ_rec) + as.factor(Quint) + lngap_perc + as.factor(year)*lngap_perc, data=clw3)

sink("output/tables/table_gapyear_int.html")
stargazer::stargazer(list(rta,rtb,rtc), type="html",
covariate.labels = c("Ed.Media", "Ed.Sup.Incomp.", "Ed.Universitaria", "Quintil 2", "Quintil 3","Quintil 2","Quintil 5", "Brecha Percibida", "Año 2009", "Año 2019", "Brecha Percibida: 2009","Brecha Percibida: 2019"),
dep.var.labels = c("Brecha Percibida", "Brecha Justa"))
sink()

@@

# Descriptivos 2

```{r}
clw3_des <- clw3 %>% select(gap_perc,gap_just,Quint,educ_rec) %>% rename("Brecha Salarial Percibida"=gap_perc,
               "Brecha Salarial Justa"=gap_just,
               "Quintil"=Quint,
               "Educacion"=educ_rec)

sink("output/tables/desc_2.html")
stargazer(clw3_des, type="html")
sink()
```
